### 2019-09-30 paper/spad_single/sections/simulation.tex
Camera alignment, distortion correction, working on supplement figure.
Updated paper figure.

\subsection{Implementation Details}
\begin{itemize}
  \item Number of bins used, depth range, laser parameters, use of intensity
    image.
  \item Using
\end{itemize}
\paragraph{NYU Depth v2}
The NYU Depth v2 Dataset consists of 249 training and 215 testing scenes of
RGB-D data captured using a Microsoft Kinect. We used a version of DORN
pretrained according to \cite{Fu2018} as our CNN.
\newpage
% \begin{table*}
% \begin{center}
% \begin{tabular}{lccc|ccc}
%   \toprule
%     & $\delta^1 \uparrow$ & $\delta^2\uparrow$ & $\delta^3 \uparrow$ & RMSE $\downarrow$ & rel $\downarrow$ & $log_{10} \downarrow$ \\
%   \midrule
% Eigen et. al. & 0.769 & 0.950 & 0.988 & 0.641 & 0.158 & - \\ 
% Laina et. al.&0.811&0.953&0.988&0.573&0.127&0.055 \\
% DORN&0.818&0.950&0.982&0.620&0.137&0.063 \\
%   DORN (rescaled) & 0.872 & 0.967 & 0.989 & 0.548 & 0.111 & 0.048 \\
% Alhashim, Wonka (2019)&0.847&0.973&0.994&0.548(0.461)&0.123&0.053 \\
% Alhashim, Wonka (2019) rescaled using GT depth"&0.888&\textbf{0.978}&\textbf{0.995}&\textbf{0.499}(0.409)&\textbf{0.106}&\textbf{0.045} \\
%   \midrule
%   Ours (raw depth counts) & \textbf{0.899} & 0.970 & 0.990 & 0.529 & 0.199 & 0.055 \\
%   Ours (DORN) (intensity/falloff) & 0.835 & 0.953 & 0.984 & 0.521 & 0.129 & 0.060 \\
%   Ours (DenseDepth) (intensity/falloff) & 0.867 & 0.974 & 0.994 & 0.445 & 0.114 & 0.050 \\
%   \bottomrule
% \end{tabular} 
% \end{center}
% \caption{Results on the NYU Depth v2 test set \cite{nyudepth}.}
% \end{table*}
%%%
\begin{table*}
\begin{center}
\input{sections/figures/sim_table.tex}
\caption{Simulated Results on NYU Depth v2. Bold indicates best performance for
  that metric, while underline indicates second best. The proposed scheme
  outperforms DenseDepth and DORN on all metrics, and even outperforms the
  median rescaling scheme, which has access to the true median depth value.}
\end{center}
\end{table*}

@@

% \begin{figure}
%   \includegraphics[width=\textwidth/2]{sections/figures/comparison.jpeg}
%   \caption{\textbf{Comparing our results with other methods}}
% \end{figure}

>>>>

\subsection{Implementation Details}
\begin{itemize}
  \item Number of bins used, depth range, laser parameters, use of intensity
    image.
  \item Using
\end{itemize}
\paragraph{NYU Depth v2}
The NYU Depth v2 Dataset consists of 249 training and 215 testing scenes of
RGB-D data captured using a Microsoft Kinect. We used a version of DORN
pretrained according to \cite{Fu2018} as our CNN.
\newpage
% \begin{table*}
% \begin{center}
% \begin{tabular}{lccc|ccc}
%   \toprule
%     & $\delta^1 \uparrow$ & $\delta^2\uparrow$ & $\delta^3 \uparrow$ & RMSE $\downarrow$ & rel $\downarrow$ & $log_{10} \downarrow$ \\
%   \midrule
% Eigen et. al. & 0.769 & 0.950 & 0.988 & 0.641 & 0.158 & - \\ 
% Laina et. al.&0.811&0.953&0.988&0.573&0.127&0.055 \\
% DORN&0.818&0.950&0.982&0.620&0.137&0.063 \\
%   DORN (rescaled) & 0.872 & 0.967 & 0.989 & 0.548 & 0.111 & 0.048 \\
% Alhashim, Wonka (2019)&0.847&0.973&0.994&0.548(0.461)&0.123&0.053 \\
% Alhashim, Wonka (2019) rescaled using GT depth"&0.888&\textbf{0.978}&\textbf{0.995}&\textbf{0.499}(0.409)&\textbf{0.106}&\textbf{0.045} \\
%   \midrule
%   Ours (raw depth counts) & \textbf{0.899} & 0.970 & 0.990 & 0.529 & 0.199 & 0.055 \\
%   Ours (DORN) (intensity/falloff) & 0.835 & 0.953 & 0.984 & 0.521 & 0.129 & 0.060 \\
%   Ours (DenseDepth) (intensity/falloff) & 0.867 & 0.974 & 0.994 & 0.445 & 0.114 & 0.050 \\
%   \bottomrule
% \end{tabular} 
% \end{center}
% \caption{Results on the NYU Depth v2 test set \cite{nyudepth}.}
% \end{table*}
%%%
\begin{figure*}[!t]
\begin{center}
\input{sections/figures/sim_table.tex}
\caption{Simulated Results on NYU Depth v2. Bold indicates best performance for
  that metric, while underline indicates second best. The proposed scheme
  outperforms DenseDepth and DORN on all metrics, and even outperforms the
  median rescaling scheme, which has access to the true median depth value. Note
that we do not report metrics for MiDaS or MiDaS with median rescaling, as MiDaS
does not output metric depth.}
\end{center}
\end{figure*}

@@
